---
title: "Chapter 2 Exercise 2"
author: "Joel"
date: "18/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Read libraries
library(readxl)
library(tsibble)
library(tsibbledata)
library(magrittr)
library(tidyverse)
library(fpp3)
```



1. Create plots of the following time series: Bricks from aus_production, Lynx from pelt, Close from gafa_stock, Demand from vic_elec.
```{r}
aus_production %>% autoplot(Bricks)
```
```{r}
pelt %>% autoplot(Lynx)
```

```{r}
gafa_stock %>% autoplot(Close)
```

```{r}
vic_elec %>% autoplot(Demand)
```

2. Use help() to find out about the data in each series.
```{r}
help("aus_production")
```
Quarterly production of selected commodities in Australia.
Description
Quarterly estimates of selected indicators of manufacturing production in Australia.

Format
Time series of class tsibble.

Details
aus_production is a half-hourly tsibble with six values:

Beer:	Beer production in megalitres.
Tobacco:	Tobacco and cigarette production in tonnes.
Bricks:	Clay brick production in millions of bricks.
Cement:	Portland cement production in thousands of tonnes.
Electricity:	Electricity production in gigawatt hours.
Gas:	Gas production in petajoules.
Source
Australian Bureau of Statistics, catalogue number 8301.0.55.001 table 1.

Examples
library(tsibble)
aus_production

```{r}
help("pelt")
```
Pelt trading records
Description
Hudson Bay Company trading records for Snowshoe Hare and Canadian Lynx furs from 1845 to 1935. This data contains trade records for all areas of the company.

Format
Time series of class tsibble

Details
pelt is an annual tsibble with two values:

Hare:	The number of Snowshoe Hare pelts traded.
Lynx:	The number of Canadian Lynx pelts traded.
Source
Hudson Bay Company

Examples
library(tsibble)
pelt

```{r}
help("gafa_stock")
```
GAFA stock prices
Description
Historical stock prices from 2014-2018 for Google, Amazon, Facebook and Apple. All prices are in $USD.

Format
Time series of class tsibble

Details
gafa_stock is a tsibble containing data on irregular trading days:

Open:	The opening price for the stock.
High:	The stock's highest trading price.
Low:	The stock's lowest trading price.
Close:	The closing price for the stock.
Adj_Close:	The adjusted closing price for the stock.
Volume:	The amount of stock traded.
Each stock is uniquely identified by one key:

Symbol:	The ticker symbol for the stock.
Source
Yahoo Finance historical data, https://finance.yahoo.com/

Examples
library(tsibble)
gafa_stock

```{r}
help("vic_elec")
```
Half-hourly electricity demand for Victoria, Australia
Description
vic_elec is a half-hourly tsibble with three values:

Demand:	Total electricity demand in MW.
Temperature:	Temperature of Melbourne (BOM site 086071).
Holiday:	Indicator for if that day is a public holiday.
Format
Time series of class tsibble.

Details
This data is for operational demand, which is the demand met by local scheduled generating units, semi-scheduled generating units, and non-scheduled intermittent generating units of aggregate capacity larger than 30 MW, and by generation imports to the region. The operational demand excludes the demand met by non-scheduled non-intermittent generating units, non-scheduled intermittent generating units of aggregate capacity smaller than 30 MW, exempt generation (e.g. rooftop solar, gas tri-generation, very small wind farms, etc), and demand of local scheduled loads. It also excludes some very large industrial users (such as mines or smelters).

Source
Australian Energy Market Operator.

Examples
library(tsibble)
vic_elec

3. For the last plot, modify the axis labels and title.
```{r}
vic_elec %>% autoplot(Demand) + labs(x="Time Base", y="Electricity Demend", title="Victoria Electricity Demand Record")
```

