---
title: "Chapter 2 Task 1"
author: "Joel"
date: "18/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Read libraries
library(readxl)
library(tsibble)
library(tsibbledata)
library(magrittr)
library(tidyverse)
library(fpp3)
```


1. Download tourism.xlsx from http://robjhyndman.com/data/tourism.xlsx, and read it into R using read_excel() from the readxl package.
```{r}
tourism <- read_excel("C:\\MSc (BDA)\\BD3P5 Econometrics lab  - Akhileshwar\\tourism.xlsx")
```

2. Create a tsibble which is identical to the tourism tsibble from the tsibble package.
```{r}
data(package = "fpp3")$results[, "Item"]
```

3. Find what combination of Region and Purpose had the maximum number of overnight trips on average.

```{r}
tourism %>% group_by(Region, Purpose) %>% summarise(total_trips = sum(Trips)/n()) %>% arrange(desc(total_trips)) %>% head(1)
```

4.Create a new tsibble which combines the Purposes and Regions, and just has total trips by State. 
```{r}
tourism %>%  mutate(Quarter = yearquarter(Quarter)) %>% as_tsibble(index = Quarter, key = c(Region, Purpose))  %>% select (-Quarter) %>% group_by(State) %>% summarise(sum(Trips))
```
```{r}
tourism %>%  select (-Quarter) %>% group_by(State) %>% summarise(sum(Trips))
 
```

