---
title: "Chapter 2 Exercise 3"
author: "Joel"
date: "18/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Read libraries
library(readxl)
library(tsibble)
library(tsibbledata)
library(magrittr)
library(tidyverse)
library(fpp3)
```

1. Look at the quarterly tourism data for the Snowy Mountains
Use autoplot(), gg_season() and gg_subseries() to explore the data.
```{r}
snowy <- tourism %>% filter(Region == "Snowy Mountains")
```


```{r}
snowy %>% mutate(Quarter = yearquarter(Quarter)) %>% as_tsibble(index = Quarter, key = c(Region, Purpose)) ->snowy_ts
snowy_ts %>%    autoplot(Trips)
```
1. The overnight trip for holidays are maximum and there is an approx 5 year cycle when it falls and then rises. Similar cyclicalness is not seen for the other purposes. There weren't many trip in 2007 which may be due to local conditions/reasons.
```{r}
help("tourism")
```


```{r}
snowy_ts %>%  gg_season(Trips)
```
2. Trips during holidays always peak in Q3 - most probably, bcos the school/college holidays happen in Q3
3. There are one odd aberrations in the other purposes, but no specific pattern emerges.
```{r}
snowy_ts %>%  gg_subseries(Trips)
```
4. The above graph corroborates the sudden rise in numbers of overnight stays in Q3.
