---
title: "Chapter2 Exercise 4"
author: "Joel"
date: "23/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Read libraries
library(readxl)
library(tsibble)
library(tsibbledata)
library(magrittr)
library(tidyverse)
library(fpp3)
```

We have introduced the following functions: gg_lag and ACF
Use these functions to explore the following time series: Bricks from aus_production
```{r}
aus_production %>% gg_lag(Bricks, geom='point')
aus_production %>% ACF(Bricks, lag_max = 100) %>% autoplot()
```
There is seasonality of 4 periods. The trend is reducing which levels out after about 80 periods. There are no cycles.


Use these functions to explore the following time series: Lynx from pelt
```{r}
pelt %>% gg_lag(Lynx, geom='point')
pelt %>% ACF(Lynx, lag_max = 100) %>% autoplot()
pelt %>% autoplot(Lynx)
```
Trend rises initially and the  decreases. Seasonality is regular at 9 periods. Ther dont seem to be any cycles.

Use these functions to explore the following time series: Victorian Electricity Demand from aus_elec
```{r}
vic_elec %>% gg_lag(Demand, geom='point')
vic_elec %>% ACF(Demand, lag_max = 100) %>% autoplot()
vic_elec %>% autoplot(Demand)
```
Trend is a mild rising trend as the demand of electricity rises every year. Seasonality is evident because of more requirement of electricity during summer and winters. Minor cyclical variations will be present.

WHich is which?
1-B, 2-A, 3-D, 4-C
```{r}

```

